Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-04-29 paper/tex/sections/appendix.tex
change comparison section
add formation channel plots
update appendix with plots/table

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
    \begin{tabular}{c|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

@@

\subsection{Detection rates}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections_fractions.pdf}
    \caption{As Figure~\ref{fig:detection_rates} except only showing the detectable \textit{fraction}.}
    \label{fig:detection_fractions}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_merging.pdf}
    \caption{The total number of merging DCOs in the Milky Way. When multiplied by Figure~\ref{fig:detection_fractions} this gives Figure~\ref{fig:detection_rates}.}
    \label{fig:total_merging_dcos}
\end{figure*}

\subsection{Miscellaneous}

\begin{figure*}[p]
    \centering
    \includegraphics[height=0.95\textheight]{previous_studies.png}
    \caption{A table of previous studies of a similar nature to this work}
    \label{fig:previous_studies}
\end{figure*}

>>>>

\subsection{Detection rate table}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
    \begin{tabular}{c|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & \confinv{34.4}{20.9}{46.6} & \confinv{29.9}{20.1}{47.4} & \confinv{7.7}{5.0}{10.3} & \confinv{58.6}{31.0}{53.3} & \confinv{51.9}{28.0}{95.0} & \confinv{13.0}{6.8}{14.2}\\
        B & \confinv{33.9}{19.7}{36.5} & \confinv{15.5}{9.6}{19.6} & \confinv{2.8}{1.9}{4.3} & \confinv{55.6}{27.7}{45.9} & \confinv{26.7}{13.8}{23.7} & \confinv{4.8}{2.7}{5.6}\\
        C & \confinv{20.6}{11.1}{20.5} & \confinv{5.3}{3.0}{5.3} & \confinv{4.3}{3.1}{5.2} & \confinv{33.7}{15.7}{26.7} & \confinv{8.9}{4.2}{7.0} & \confinv{7.3}{4.5}{6.1}\\
        D & \confinv{21.9}{14.7}{37.8} & \confinv{4.1}{2.6}{4.2} & \confinv{11.6}{8.3}{22.7} & \confinv{36.0}{21.6}{45.4} & \confinv{6.8}{3.4}{5.3} & \confinv{20.5}{12.7}{27.7}\\
        E & \confinv{33.7}{19.4}{37.0} & \confinv{3.3}{2.3}{6.3} & \confinv{0.2}{0.1}{0.1} & \confinv{54.9}{26.7}{44.2} & \confinv{5.8}{3.5}{8.2} & \confinv{0.3}{0.1}{0.2}\\
        F & \confinv{26.2}{16.0}{35.8} & \confinv{15.0}{11.4}{84.0} & \confinv{5.7}{3.8}{7.3} & \confinv{43.3}{22.2}{43.7} & \confinv{27.2}{18.2}{86.3} & \confinv{9.5}{5.2}{10.0}\\
        G & \confinv{29.5}{15.9}{27.6} & \confinv{23.5}{14.0}{27.2} & \confinv{23.4}{15.2}{27.9} & \confinv{47.5}{21.4}{38.3} & \confinv{40.9}{20.7}{36.3} & \confinv{39.8}{21.4}{36.3}\\
        H & \confinv{115.1}{98.0}{123.0} & \confinv{30.7}{21.4}{163.7} & \confinv{7.4}{4.8}{14.6} & \confinv{173.6}{117.7}{150.5} & \confinv{55.4}{32.8}{185.8} & \confinv{13.0}{6.8}{25.5}\\
        I & \confinv{22.7}{12.4}{26.8} & \confinv{48.7}{30.9}{97.1} & \confinv{6.3}{4.0}{9.0} & \confinv{36.1}{16.8}{30.8} & \confinv{84.0}{45.0}{142.8} & \confinv{10.9}{5.8}{11.1}\\
        J & \confinv{47.5}{31.6}{71.9} & \confinv{24.3}{16.3}{37.4} & \confinv{6.8}{4.4}{10.9} & \confinv{80.7}{46.8}{86.8} & \confinv{41.7}{22.9}{47.0} & \confinv{11.6}{6.2}{14.0}\\
        K & \confinv{30.1}{18.0}{40.4} & \confinv{37.6}{24.6}{44.9} & \confinv{7.8}{5.1}{11.6} & \confinv{52.5}{28.2}{48.4} & \confinv{65.1}{35.0}{54.7} & \confinv{13.4}{7.1}{14.8}\\
        L & \confinv{35.2}{21.3}{45.2} & \confinv{30.2}{19.9}{49.6} & \confinv{7.9}{5.0}{11.7} & \confinv{58.9}{31.0}{54.9} & \confinv{52.4}{28.5}{96.9} & \confinv{13.3}{7.1}{14.8}\\
        M & \confinv{43.0}{28.3}{58.3} & \confinv{68.7}{43.4}{108.7} & \confinv{16.1}{10.4}{20.5} & \confinv{69.4}{38.1}{69.1} & \confinv{117.4}{61.8}{154.5} & \confinv{27.3}{14.5}{26.4}\\
        N & \confinv{53.0}{34.1}{58.3} & \confinv{110.6}{71.3}{193.1} & \confinv{35.7}{23.6}{54.8} & \confinv{84.4}{44.9}{73.3} & \confinv{194.9}{102.6}{256.0} & \confinv{60.2}{32.7}{67.8}\\
        O & \confinv{43.1}{27.0}{39.0} & \confinv{76.0}{43.9}{91.2} & \confinv{9.3}{6.0}{10.4} & \confinv{68.5}{35.8}{47.5} & \confinv{130.8}{62.9}{122.0} & \confinv{15.8}{8.4}{13.8}\\
        P & \confinv{44.3}{28.4}{62.2} & \confinv{26.7}{17.0}{48.9} & \confinv{9.0}{5.6}{10.9} & \confinv{69.9}{38.0}{78.9} & \confinv{45.9}{25.9}{64.4} & \confinv{15.3}{7.4}{13.9}\\
        Q & \confinv{0.0}{0.0}{0.0} & \confinv{6.3}{3.7}{6.1} & \confinv{7.8}{4.7}{8.0} & \confinv{0.0}{0.0}{0.0} & \confinv{10.8}{5.3}{7.6} & \confinv{13.0}{6.4}{10.4}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

@@

\subsection{Formation channels}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{formation_channels_BHBH.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{formation_channels_BHNS.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{formation_channels_NSNS.pdf}
\end{figure}
